---
title: "Post-vaccination Accident and Emergency Department Attendances"
output:
  #github_document:
  #  keep_html: TRUE
  #  code_folding: hide
  #  keep_md: yes
  #pdf_document: default
  #md_document:
  #   variant: gfm
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}

library('tidyverse')
library('here')
library('glue')
library('lubridate')
library('gt')
library('patchwork')


output_dir <- here("output")

fs::dir_create(output_dir, "report", "figures")

knitr::opts_chunk$set(
  echo = TRUE,
  fig.path = paste0(fs::path(output_dir, "report", "figures"), "/")
)

studydates <- jsonlite::read_json(
  path=here("analysis", "lib", "dates.json")
)

lookup <- read_rds(here("analysis", "lib", "diagnosis_groups_lookup.rds")) 

```

# Introduction

Three vaccines have been used as part of the national COVID-19 vaccination programme in England to date: Pfizer-BioNTech BNT162b2 mRNA (*BNT162b2*), Oxford-AstraZeneca ChAdOx1 nCoV-19 (*ChAdOx1*), and Moderna mRNA-1273 (*Moderna*). This report describes rates of attendances to accident and emergency departments (A&E) in the first 2 weeks following the first dose of these vaccines. 

The code and data for this report can be found at the OpenSafely [post-vax-ae_attendances GitHub repository](https://github.com/opensafely/post-vax-ae-attendances). 


# Methods

People meeting the following criteria are included:

* People receiving their ever first vaccine dose as part of the national COVID-19 vaccination programme (i.e., not administered in clinical trials):
  * BNT162b2 received on or after `r format(as.Date(studydates$start_date_pfizer), "%d %B %Y")`;
  * ChAdOx1 received on or after `r format(as.Date(studydates$start_date_az), "%d %B %Y")`;
  * Moderna received on or after `r format(as.Date(studydates$start_date_moderna), "%d %B %Y")`.
* Registered at a GP practice using TPP's SystmOne clinical information system on the day before vaccination.
* Aged 16 or over.

The vaccination brand is available in the GP record directly, via the National Immunisation Management System (NIMS).

A&E attendances are identified using linked data from the Emergency Care Data Set (ECDS) provided by NHS Digital's Secondary Use Service (SUS), which holds records on all attendances to A&E departments. For each A&E attendance, one or more diagnosis codes are recorded. These have been categorised into `r nrow(lookup)` categories, detailed below.

Vaccine recipients are classified into one of the [10 vaccine priority groups defined by the Joint Committee on Vaccination and Immunisation (JCVI)](https://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/1007737/Greenbook_chapter_14a_30July2021.pdf#page=12) expert working group. These are based on demographic, clinical, or occupational characteristics identified on or before the vaccination date, except for age, which is determined as of 31 March 2020.

# Results

Note all counts below 6 are redacted and survival estimates are rounded for disclosure control.

## Characteristics as at vaccination date

### Overall
```{r table1, echo=FALSE}
read_rds(here("output", "table1", "table1.rds"))
```


## Vaccination dates


### Overall
```{r, vaxdate, echo=FALSE, message=FALSE, warning=FALSE, out.width='80%', results='asis'}
  vaxdate_plot <- read_rds(here("output", "vaxdate", "plot_vaxdate_stack.rds"))
  print(vaxdate_plot)
  cat("  \n\n")
```

### By JCVI priority group

```{r, vaxdate_jcvi, echo=FALSE, message=FALSE, warning=FALSE, out.width='80%', fig.height=8, results='asis'}
  vaxdate_plot <- read_rds(here("output", "vaxdate", "plot_vaxdate_stack_jcvi.rds"))
  print(vaxdate_plot)
  cat("  \n\n")
```

## A&E attendances

### Overall

```{r, surv, echo=FALSE, message=FALSE, warning=FALSE, out.width='80%', results='asis'}
  surv_plot <- read_rds(here("output", "diagnoses", "plot_surv.rds"))
  print(surv_plot)
  cat("  \n\n")
```

### Diagnosis-specific attendances

```{r, surv_diagnosis, echo=FALSE, message=FALSE, warning=FALSE, out.width='80%', fig.height=6, results='asis'}
  surv_plot <- read_rds(here("output", "diagnoses", "plot_diagnosis_surv.rds"))
  print(surv_plot)
  cat("  \n\n")
```


### Diagnosis-specific attendances, by JCVI group

```{r, surv_diagnosis_jcvi, echo=FALSE, message=FALSE, warning=FALSE, out.width='80%',fig.height=8, results='asis'}
  surv_plot <- read_rds(here("output", "diagnoses", "plot_diagnosis_surv_jcvi.rds"))
  print(surv_plot)
  cat("  \n\n")
```


### Diagnosis-specific attendances, by month of vaccination

```{r, surv_diagnosis_month, echo=FALSE, message=FALSE, warning=FALSE, out.width='80%', fig.height=8,  results='asis'}
  surv_plot <- read_rds(here("output", "diagnoses", "plot_diagnosis_surv_month.rds"))
  print(surv_plot)
  cat("  \n\n")
```

